---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setupREADME, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RmdConcord

<!-- badges: start -->
<!-- badges: end -->

**NB:  development has for now moved to the `patchDVI` project at https://github.com/dmurdoch/patchDVI/tree/RmdConcord. 
The installation instructions have been updated to reflect that
change, but the rest of the
code in this repository has not!**


The goal of RmdConcord is to provide support for concordances
in R Markdown files.

This is based on a suggestion and initial code from Heather Turner.
Thanks!

The main use for this in HTML output is to help deciphering HTML Tidy
error messages.  If you replace the original driver with this one, 
`R CMD check` should report locations in the original `.Rmd` file.

With PDF output, this will enable Synctex output, and patch it
to refer to the `.Rmd` file.  This is helpful in previewers like
the one in TeXworks that can link source to a preview.

## Installation

This version of `RmdConcord` makes use of some functions that
will be released in R 4.3.0.  They are available in a development
version of the `backports` package.

It also requires patches to `knitr` to support concordances in
R Markdown files.  These are also currently in a development version 
of that package.

You can install the development version of RmdConcord from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dmurdoch/backports")
devtools::install_github("dmurdoch/knitr")
devtools::install_github("dmurdoch/patchDVI@RmdConcord")
```

## Example

To embed concordances in an R Markdown HTML document, change
the output YAML to `patchDVI::html_documentC`.  For a PDF document,
use `patchDVI::pdf_documentC`.

```yaml
output: patchDVI::html_documentC
```

This is used in the `Sample.Rmd` vignette.

```{r example}
library(RmdConcord)
example(processConcordance)
```
