---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setupREADME, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RmdConcord

<!-- badges: start -->
[![R-CMD-check](https://github.com/dmurdoch/RmdConcord/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/dmurdoch/RmdConcord/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of RmdConcord is to provide support for concordances
in R Markdown files.

This is based on a suggestion and initial code from Heather Turner.
Thanks!

The main use for this in HTML output is to help deciphering HTML Tidy
error messages.  If you replace the original driver with `patchDVI::html_documentC`, 
`R CMD check` should report locations in the original `.Rmd` file.

With PDF output using `patchDVI::pdf_documentC`, Synctex output will be enabled, and it will be patched
to refer to the `.Rmd` file.  This is helpful in previewers like
the one in TeXworks that can link source to a preview.

The `RmdConcord` package also has drivers with the 
same names as the ones described above.  These are
intended to be used by other packages rather than
directly by users:  they will leave concordance
records in the file for later handling.


## Installation

This version of `RmdConcord` makes use of some functions that
will be released in R 4.3.0.  They are available in a development
version of the `backports` package.

You can install the development version of RmdConcord from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dmurdoch/backports")
devtools::install_github("dmurdoch/RmdConcord")
```

## Example

To embed concordances in an R Markdown HTML document, change
the output YAML to `patchDVI::html_documentC`.  For a PDF document,
use `patchDVI::pdf_documentC`.

```yaml
output: patchDVI::html_documentC
```

This is used in the `Sample.Rmd` vignette.

```{r example}
library(RmdConcord)
example(processConcordance)
```
