---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# RmdConcord

<!-- badges: start -->
<!-- badges: end -->

The goal of RmdConcord is to provide support for concordances
in R Markdown files.

This is based on a suggestion and initial code from Heather Turner.
Thanks!

## Installation

This version of `RmdConcord` makes use of some functions that
will be released in R 4.3.0.  They are available in a development
version of the `backports` package.

You can install the development version of RmdConcord from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dmurdoch/backports)
devtools::install_github("dmurdoch/RmdConcord")
```

## Example

To embed concordances in an R Markdown HTML document, change
the output YAML to `RmdConcord::html_commonmark_document`.

```{yaml example}
output: RmdConcord::html_commonmark_document
```

This is used in the `Sample.Rmd` vignette.

```{r}
library(RmdConcord)
example(getDataposConcordance)
```
